Comparing summed probability distributions of shoreline and radiocarbon dates from the Mesolithic Skagerrak coast of Norway

### 2023-08-11 analysis/paper/paper.Rmd
Minor edits

To what degree the radiocarbon record is determined by past population numbers might vary geographically and chronologically, based on variation in investigatory and taphonomic factors [@surovell2009b; @bluhm2019], as well as cultural processes within prehistoric populations. One example of the latter is the difference that might exist between farmer and forager populations, where @freeman2018 have suggested that an increased per capita energy consumption introduced with farming means that ^14^C-dates should not be weighted equally when making relative population estimates across such populations. Similarly, while site counts have also been invoked for the analysis of past population dynamics, these are likely to be impacted by factors such as land-use and mobility patterns, and settlement nucleation and dispersion, as well as variation in archaeological investigations and what has been taken to constitute a 'site' [@palmisano2017]. However, these could be considered theoretical issues that have implications for how fluctuations in these proxies should be interpreted, and possibly weighted differently according some criteria. Before any such fluctuations are given any substantive interpretation, however, there is a host of methodological issues that have to be considered [see @carleton2021; @crema2022 for reviews].

>>>>

To what degree the radiocarbon record is determined by past population numbers might vary geographically and chronologically, based on variation in investigatory and taphonomic factors [@surovell2009b; @bluhm2019], as well as cultural processes within prehistoric populations. One example of the latter is the difference that might exist between farmer and forager populations, where @freeman2018 have suggested that an increased per capita energy consumption introduced with farming means that ^14^C-dates should not be weighted equally when making relative population estimates across such populations. Similarly, while site counts have also been invoked for the analysis of past population dynamics, these are likely to be impacted by factors such as land-use and mobility patterns, and settlement nucleation and dispersion, as well as variation in archaeological investigations and what has been taken to constitute a 'site' [@crema2020; @palmisano2017]. However, these could be considered theoretical issues that have implications for how fluctuations in these proxies should be interpreted, and possibly weighted differently according some criteria. Before any such fluctuations are given any substantive interpretation, however, there is a host of methodological issues that have to be considered [see @carleton2021; @crema2022 for reviews].
